### 2013-02-16 doc/icml2013/discussion.tex
changes

\section{Discussion}
\label{sec:discussion}

Role of spectral algorithms in discriminative tasks.

Challenges and ways forward?

>>>>

\section{Conclusion}
\label{sec:conclusion}

In this paper, we take a first step at developing computationally efficient and
statistically consistent estimators for discriminative latent-variable models
by focusing on mixture of linear regressions. We showed that by regressing on
higher-order powers of the data with a regularizer that encourages low rank
structure, coupled with an efficient tensor power method, we obtain a very natural algorithm.
Empirically, our algorithm can outperform EM, and when used to initialize EM,
yields significantly more accurate and stable results.

### 2013-02-16 doc/icml2013/evaluation.tex
edit
changes

\begin{figure*}[t]
  \centering
  \subfigure[Spectral]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-specm.pdf}}
    \hspace{-2em}
  \subfigure[EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-em.pdf}}
%  \subfigure[Spectral + EM]{
%    \includegraphics[width=0.34\textwidth]{figures/curves-vis/1-8-3-spem.png}}
  \caption{A comparison between SpectralExperts and EM. The dashed lines
  on the left denote the solution recovered by Spectral Experts. Whilst
  not a perfect fit, it provides an good initialization for EM to find
  the true global minima. The dotted lines on the right show different
  local optima found by EM on this example.}
  \label{fig:curves}
\end{figure*}

@@

\begin{table*}[t]
\caption{Parameter Recovery Error $\|\theta^* - \hat \theta\|_F$ ($N = 500,000$).}
\label{tbl:parameter-recovery}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}

@@

\begin{figure}[tb]
  \centering
  \includegraphics[width=0.50\textwidth]{figures/hist.pdf}
  \caption{Histogram over recovery errors between the three algorithms. $b = 1, d = 4, k = 3, N = 500,000$}
  \label{fig:hist}
\end{figure}

To study the stability of the solutions returned by the spectral method,
consider the histogram in \figureref{fig:hist}, which shows the recovery
errors of the algorithms over 170 attempts a dataset with $b = 1, d = 4,
k = 3$. Typically, the spectral algorithm returned a stable solution.
When these parameters were close enough to the true parameters, we found
that EM almost always converged to the global optima. Randomly
initialized EM only finds the true parameters a little over 10\% of the
time and shows considerably higher variance.

@@

\begin{figure*}[tb]
  \centering
  \subfigure[Well Data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1833-decay.pdf}
  }
    \hspace{-2em}
  \subfigure[Misspecified Data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1-8-3-3-rm.pdf}
  }
  \caption{Recovey error vs $n$  ($b = 1, d = 5, K = 3, N = 500,000$).}
  \label{fig:vs-n}
\end{figure*}

In \figureref{fig:vs-n}, we show how the recovery error varies as we get
more data. Each data point shows the mean error over 10 attempts, with
error bars. We note that the recovery performance of EM does not
particularly improve; this is expected because of the problem of local
optima. The spectral algorithm's error decays slowly, and as it gets
closer to zero, EM initialized at the spectral parameters finds the true
parameters more often as well. This behaviour highlights the trade-off
between statistical and computational error.

@@

\begin{table*}[tb]
\caption{Parameter Recovery Error $\|\theta^* - \hat \theta\|_F$ with misspecified data ($N = 500,000$).}
\label{tbl:parameter-recovery-mis}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}

>>>>

\begin{figure*}[p]
  \centering
  \subfigure[Spectral]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-specm.pdf}}
    \hspace{-2em}
  \subfigure[EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-em.pdf}}
%  \subfigure[Spectral + EM]{
%    \includegraphics[width=0.34\textwidth]{figures/curves-vis/1-8-3-spem.png}}
  \caption{A comparison between SpectralExperts and EM. The dashed lines
  on the left denote the solution recovered by Spectral Experts. Whilst
  not a perfect fit, it provides an good initialization for EM to find
  the true global minima. The dotted lines on the right show different
  local optima found by EM on this example.}
  \label{fig:curves}
\end{figure*}

@@

\begin{table*}[p]
\caption{Parameter Recovery Error $\|\theta^* - \hat \theta\|_F$ ($N = 500,000$).}
\label{tbl:parameter-recovery}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}

@@

\begin{figure}[th]
  \centering
  \includegraphics[width=0.50\textwidth]{figures/hist.pdf}
  \caption{Histogram over recovery errors between the three algorithms. $b = 1, d = 4, k = 3, N = 500,000$}
  \label{fig:hist}
\end{figure}

To study the stability of the solutions returned by the spectral method,
consider the histogram in \figureref{fig:hist}, which shows the recovery
errors of the algorithms over 170 attempts on a dataset with $b = 1, d = 4,
k = 3$. Typically, the spectral algorithm returned a stable solution.
When these parameters were close enough to the true parameters, we found
that EM almost always converged to the global optima. Randomly
initialized EM only finds the true parameters a little over 10\% of the
time and shows considerably higher variance.

@@

\begin{figure*}[p]
  \centering
  \subfigure[Well Data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1833-decay.pdf}
  }
    \hspace{-2em}
  \subfigure[Misspecified Data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1-8-3-3-rm.pdf}
  }
  \caption{Recovery error vs $n$  ($b = 1, d = 5, K = 3, N = 500,000$).}
  \label{fig:vs-n}
\end{figure*}

In \figureref{fig:vs-n}, we show how the recovery error varies as we get
more data. Each data point shows the mean error over 10 attempts, with
error bars. We note that the recovery performance of EM does not
particularly improve; this suggests that EM continues to get stuck in
a local optima. The spectral algorithm's error decays slowly, and as it
gets closer to zero, EM initialized at the spectral parameters finds the
true parameters more often as well. This behavior highlights the
trade-off between statistical and computational error.

@@

\begin{table*}[t]
\caption{Parameter Recovery Error $\|\theta^* - \hat \theta\|_F$ with misspecified data ($N = 500,000$).}
\label{tbl:parameter-recovery-mis}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}
